Timeliness of security updates for Android

### 2014-11-14 securityupdates.tex
Updated dastats for more consistent reporting of numbers

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing that, on average, \daMeanInsecurityPerc\ of Android devices are exposed to critical vulnerabilities.
Devices, on average, apply \daUpdatesPerYear\ updates each year and \daPercUpdatesDowngrades\ of version changes are downgrades to older versions.
Nexus devices are better than others, \emph{\daSecScoreBestmanufacturer} is the highest scoring device manufacturer and \emph{\daSecScoreBestoperator} is the highest scoring network operator.
%\todo{comparison of nexus update rates with iOS}
We describe four experiments.
We examine the vulnerability of the Android ecosystem as a whole (\S\ref{sec:exp:versionsecurity}, explore the upgrade cycle and vulnerability cycle of the ecosystem (\S\ref{sec:exp:android_ecosystem}), quantify the updates installed on particular devices (\S\ref{sec:exp:device_updates}) and compare the performance of different device manufacturers and network operators (\S\ref{sec:exp:security_score}).

@@

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the \da\ data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/nw_security_updates.pdf}
 \caption{Proportion of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
We recorded update events and Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Mostly the dark cells are upgrades (above the diagonal) (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number (\daNumUpdatesBigUpgrades, \daPercBigUpgrades) which skip more than \daNumUpdatesSkippedBig\ versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngrades) when older versions of Android are installed on to devices.
Possible reasons why users are downgrading are to free up space on their device, to make it easier to root or because a new version introduced bugs.

>>>>

\section{Experiments}
\label{sec:results}
We present the results of our analysis showing that, on average, \daMeanInsecurityPerc\ of Android devices are exposed to critical vulnerabilities.
Devices, on average, apply \daUpdatesPerYear\ updates each year and \daPercUpdatesDowngrades\ of full version changes are downgrades to older versions.
Nexus devices are better than others, \emph{\daSecScoreBestmanufacturer} is the highest scoring device manufacturer and \emph{\daSecScoreBestoperator} is the highest scoring network operator.
%\todo{comparison of nexus update rates with iOS}
We describe four experiments.
We examine the vulnerability of the Android ecosystem as a whole (\S\ref{sec:exp:versionsecurity}, explore the upgrade cycle and vulnerability cycle of the ecosystem (\S\ref{sec:exp:android_ecosystem}), quantify the updates installed on particular devices (\S\ref{sec:exp:device_updates}) and compare the performance of different device manufacturers and network operators (\S\ref{sec:exp:security_score}).

@@

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the \da\ data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/nw_security_updates.pdf}
 \caption{Proportion of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
We recorded update events and Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Mostly the dark cells are upgrades (above the diagonal) (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number (\daNumUpdatesBigUpgrades, \daPercBigUpgradesNominal) which skip more than \daNumUpdatesSkippedBig\ versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngradesNominal) when older versions of Android are installed on to devices.
Possible reasons why users are downgrading are to free up space on their device, to make it easier to root or because a new version introduced bugs.
